Diffusive Nested Sampling: Not Dead Yet

### 2025-08-29 talk/talk.tex
Edited slide

\begin{frame}
\frametitle{Thermodynamic Integration}
An older technique to calculate $P(M\given D)$ is based on the following
result:
\begin{align}
\log Z &= \int_0^1 \left<\log L(\theta)\right>_\beta \, d\theta
\end{align}
\pause
where the expectation is taken with respect to `power posteriors'
proportional to $\pi(\theta)L(\theta)^\beta$. An `annealing' process can be done
where $\beta$ is gradually raised from 0 to 1.

>>>>

\begin{frame}
\frametitle{Thermodynamic Integration}
An older technique to calculate $Z$ is based on the following
result:
\begin{align}
\log Z &= \int_0^1 \left<\log L(\theta)\right>_\beta \, d\theta
\end{align}
\pause
where the expectation is taken with respect to `power posteriors'
proportional to $\pi(\theta)L(\theta)^\beta$. \\[0.5em]\pause

An `annealing' process can be done
where $\beta$ is gradually raised from 0 to 1. As a side effect, difficult
posteriors such as those with multiple peaks become a bit easier.
